---
title: "Alcohol vs Seat choice"
author: "Ashley Saunders"
date: "Fall 2024 "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot
```{r}
boxplot(alcohol~Seat,data=davisdata)
```

The median for the back box is greater than the other, middle and front, boxes. While the front and middle both are similar, the middle box has a much greater amount of outliers. Also, these boxes are not disjoint.


```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
From this data, we can see that the front and back seats have roughly the same amount of people, while the back seat has over twice the amount. This evidence makes it clear that while the back seat had 32 people, they had a max of 55 drinks. This would be around twice the amount of the front and middle seats. The back seat has a mean of 9.6 and the front has about 2 and the back has a median of 4.   

## Inferential Tests

## Conclusions


